The globular cluster system of the Auriga simulations

### 2020-04-11 response_to_referee.tex

\documentclass{article}

\begin{document}

\section*{Introduction}
We thank the referee for a thoughtful and elaborate report. We address the 
comments in sections with headings that match those of the referee report, 
starting with the following listing of our response to the 3 paragraphs in 
the introduction.
\begin{enumerate}
\item We updated the abstract and conclusion to clarify that we meant to describe
what would be needed for the environmental dependence of the formation and disruption
of bound clusters for the Auriga simulations to be consistent with the observations,
rather than to argue that the Auriga simulations reflect these trends.
\item
We feel that our conclusion would be too strongly phrased if we would generalise 
our results obtained using the Auriga simulations to cosmological simulations 
in general. We find that age-selected stellar particles in the Auriga simulations 
do not reproduce key properties of observed GC systems in the Milky Way and M31.
However, our results might reflect characteristics that are specific to Auriga, 
e.g. that the galaxy formation model overmixes metals at early times. 
Therefore we did add a final bulletpoint to our conclusion to clarify the above, 
but we limit the scope to the Auriga simulations. Thanks for pointing this out!

@@

\section*{Comments for each section}
\subsection*{Introduction}
\begin{itemize}
\item Item
\end{itemize}

\subsection*{Sect. 2 -}
\begin{itemize}
\item We added the halo mass range of the Auriga simulations.
\item The last paragraph should now make more sense after updating the introduction.
\end{itemize}

\subsection*{Sect. 3 -}
\begin{itemize}
\item We added references to section 3.3, 3.4, and 3.5 in the first paragraph of section 3.
\item Section 3.2 has been restructured.
\item We removed the standard error on the mean and replaced `dispersion' 
by `standard deviation' in section 3.3.
\item We added a sentence to clarify the last statement in section 3.4.
\end{itemize}

\subsection*{Sect. 4 -}
\begin{itemize}
\item We added the mean number of GC candidates compared to the mean number of
star particles in the Auriga L4 galaxies. In addition, Figure 3 now shows the 
number of star particles included in each subset.
\item We clarified at various places whether we mean the mean or median among
the simulations, or if we refer to the absolute value of one of the galaxies.
\item We added the suggestion in the 3rd paragraph of section 4.1.
\item Bimodality in GC systems is now discussed in the introduction.
\item Figure 4 - now has a vertical line to indicate the metallicity cut 
between metal-poor and metal-rich GC subpopulations in the Milky Way.
\item We added a sentence about the cluster formation efficiency model of 
Kruijssen (2012) in the last paragraph of section 4.1.
\item We now show the median instead of the mean for the galactocentric radius in
section 4.2 and Figure 6.
\item Figure 6: no changes were made for rescaling the galaxies (i.e. we still
use the virial radius)
\item Figure 5 and 7: shaded regions now show the 25-75th percentiles.
\item We added a brief discussion of Figure 8.
\item We clarified that we are referring to Figure 5 and Figure 7 for the claims about
the {\it in situ} and accreted component in the third paragraph of section 4.3.
\item Figure 9: The values are removed from the masked upper right corner bins.
\item Figure 2,8,9: The values of the upper and right axes have been removed from
Figure 2 and 9 (observations) for clarity (rather than the suggestion to add 
axis labels and units). However, we did not mask these bins for Figure 8 (Auriga)
because it illustrates our finding that the simulations produce a considerable
amount of mass in GC candidates with low metallicities at large radii.
\end{itemize}

\subsection*{Sect. 5 -}
\begin{itemize}
\item We added references to Deason et al. (2015) and Conroy et al. (2019) in
the first paragraph of section 5.1.
\item TODO: bimodality in SLUGGS
\item We still find that the accreted star particles are more metal-poor than 
those that have formed {\textit in situ} if we lower the age cut to 8 or 6 Gyr.
This has been added in section 5.3.
\item We removed the quoted sentence.
\item We clarified that our selection function is inconsistent with the definition
\item We clarified which which galaxy Brodie \& Strader provide the quoted number.
\item We clarified footnote 8.
of Kruijssen (2019) for {\textit ex. situ} GC formation.
\end{itemize}

### 2020-04-11 AurigaGCS.tex
Minor updates

TODO: ``\citet{2012MNRAS.426.1475U} shows the great variety in GC metallicity distributions
present in the sample of early-type galaxies of the SLUGGS survey contradicts
the classical idea that all the metallicity distributions of GCs should be bimodal.''

@@

The analysis in this work was performed using the Python \citep{python}
programming language, the IPython \citep{2007CSE.....9c..21P} environment, 
the NumPy \citep{2011CSE....13b..22V}, SciPy \citep{scipy}, and Astropy 
\citep{2013A&A...558A..33A} packages. Plots were created with Matplotlib 
\citep{2007CSE.....9...90H}, using the perceptually uniform colour maps
from \citet{2015arXiv150903700K} for two-dimensional plots.

>>>>

% Referee: ``\citet{2012MNRAS.426.1475U} shows the great variety in GC metallicity distributions
% present in the sample of early-type galaxies of the SLUGGS survey contradicts
% the classical idea that all the metallicity distributions of GCs should be bimodal.''

@@

The analysis in this work was performed using the Python \citep{python}
programming language, the IPython \citep{2007CSE.....9c..21P} environment, 
the NumPy \citep{2011CSE....13b..22V}, SciPy \citep{scipy}, and Astropy 
\citep{2013A&A...558A..33A} packages. Plots were created with Matplotlib 
\citep{2007CSE.....9...90H}, using the perceptually uniform colour maps
from \citet{2015arXiv150903700K} for two-dimensional plots. This research 
has made use of NASA's Astrophysics Data System Bibliographic Services.
